%------------------------
% Resume Template
% Author : Ankit Rana
% Github : https://github.com/anartikna
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{siunitx}
\usepackage[T1]{fontenc}
\usepackage[]{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
\usepackage{textcomp}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage{fontawesome}



% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\publication}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\extracurricular}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}
%-------THIS DETERMINES THE HEADINGS STYLING
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\sisetup{math-micro=\text{µ},text-micro=µ}

\fancyhf{}
\cfoot{\thepage}
\pagestyle{fancy} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------

\begin{center}
{\Huge Ankit Rana}\par\bigskip
\begin{minipage}[b]{0.33333\textwidth}
\raggedright
\faMapMarker {~~San Diego, CA} \par
\faLinkedin {~~linkedin.com/in/ranaat/}
\end{minipage}%
\begin{minipage}[b]{0.33333\textwidth}
\centering
\faEnvelope {~~arana@illumina.com} \par
\end{minipage}%
\begin{minipage}[b]{0.33333\textwidth}
\raggedleft
 \par
 \faPhone {~~+1-858-380-6282}
\faGithub  {~~github.com/ank1trana}
\end{minipage}
\end{center}

\vspace{5pt}
%----------PROFESSIONAL EXPERIENCE SECTION-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
		{Illumina, Inc.}{San Diego, CA}
		{Scientist 2}{Oct 2020 - Present}
		\resumeItemListStart [leftmargin=*]
        \resumeItem{Research}{ Single molecule experimentation aimed at a novel sequencing platform development.}
        \resumeItem{System development}{Development of recipes to govern the application of electrical waveforms and control fluidic valves and pumps in the sequencing platform. Writing python scripts to perform a variety of data analysis operations.}
        \resumeItem{Biochemistry}{Sample preparation encompassing reagent dilutions, DNA construct annealing and Agarose gel based quality control.}
		\resumeItemListEnd
  
    \resumeSubheading{Ontera, Inc. \textit{(formerly Two Pore Guys, Inc.)}}{Santa Cruz, CA}
    {R\&D Engineer}{Mar 2018 - Sep 2020}
    \resumeItemListStart [leftmargin=*]
        \resumeItem{Nanofabrication}
          {Photolithography, plasma bonding \& wet-etching in the fabrication of the dual nanopore chip.}
          \resumeItem{Experimentation}
          {Assembly of the microfluidic dual nanopore device; design of Experiments (DOE) and data analysis using MATLAB around the two-pore control (Epigenetics application).}
          \resumeItem{Controller Design}{Development of LabVIEW FPGA control for DNA linearization and bidirectional ‘flossing’ and re-capture of detected single molecules.}
          \resumeItem{Inventory and Quality Control}{Conducting optical QC of the fabricated nanopore chips, dicing of the wafer post-fab, electrical failure detection of pores, microfluidic-strip fault analysis, Agarose gel electrophoresis and imaging}
      \resumeItemListEnd

    \resumeSubheading
		{Aricent Inc. (Now Altran Group)}{Gurugram, HY}
		{Software Engineer}{Dec 2013 -  Jul 2015}
		\resumeItemListStart [leftmargin=*]
        \resumeItem{BluWAN EMS - Ethernet Switch Configuration Solution}
          {Formulated the front-end UI design with HTML, CSS, and AngularJS and back-end servlets in Java for an EMS solution (SNMP configuration).}
        \resumeItem{Mantu - Secure Enterprise Chat Application}
          {Part of a 2 member server-team. Engineered modules for UI Interface at the Ejabberd XMPP server, OTP generation, SSL verification and file storage in Erlang.}
		\resumeItemListEnd
		
	

\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Texas at Austin}{Austin, TX}
      {Master of Science in Computer Science}{Aug 2020 - May 2023}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Machine Learning, Deep Learning, Natural Language Processing, Online Learning and Optimization, Algorithms, Advanced Operating Systems, Virtualization, Android Programming, Quantum Information Science.}}}
      
    \resumeSubheading
      {College of Engineering and Applied Science, University of Cincinnati}{Cincinnati, OH}
      {Master of Science in Electrical Engineering}{Aug 2015 - Dec 2018}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Thesis:} A study of electrokinetics in glass nanopores for biomolecular applications. \bf {Adviser:}}Dr. Leyla Esfandiari}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Biomedical Microsystems, Microfabrication of Semiconductor Devices, Microelectromechanical Systems, Biochip/Lab-on-a-Chip, Bio-microfluidics.}}}
       \resumeSubheading
      {Guru Gobind Singh Indraprastha University}{New Delhi, DL}
      {Bachelor of Technology in Electronics and Communication Engineering;  GPA: 80.1}{Aug 2009 - May 2013}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Programming in C, Database Management Systems (SQLite), Embedded Systems, Circuits \& Systems, Analog and Digital Electronics, VLSI Design.}}}
      
       \resumeSubheading
      {Massive Online Open Courses (MooC) certifications}{Online}
      {edX \& Coursera}{}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Key Courses:} Python for Everybody (UMich)-Coursera, Data Structures in Python(Coursera), Linux – edX (Linux Foundation), Descriptive Statistics – edX (UC Berkeley), Introduction to Computing technology inside your smartphone – edX (Cornell University),Embedded Systems – edX (UT Austin) \& Fundamentals of Nano-electronics – edX (Purdue University)}}}
    \resumeSubHeadingListEnd
	 
%-----------skills section-----------------	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\vspace{2pt}
	\resumeSubItem{Platforms}{Linux, Windows, 8051\si{\micro C}, Arduino, Raspberry Pi.}
	\vspace{2pt}
	\resumeSubItem{Programming languages}{Python, Java, Kotlin, C, C++, Erlang, JavaScript, SQLite, AngularJS, HTML, CSS.}
	\vspace{2pt}
	\resumeSubItem{Fabrication and metrology}{Mask design, Photolithography, Wet etching, Reactive Ion etching (RIE), Soft Lithography, Fluorescent and confocal microscopy, CO\textsubscript{2} laser pulling, Plasma bonding, Spectroscopy (Ellipsometry), SEM.}
	\vspace{2pt}
	\resumeSubItem{Molecular biology}{Protein tagging
of DNA molecules, Agarose Gel Electrophoresis, Polymerase Chain Reaction (qPCR), Dynamic light scattering (DLS), Microparticles conjugation (Surface chemistry), Nanodrop, Spectrophotometry.}
\vspace{2pt}
	\resumeSubItem{Design tools}{MATLAB, COMSOL Multiphysics, CFD-GEOM \& Ace+, SolidWorks, AutoCAD, ANSYS Fluent, LabVIEW, Adobe Design Suite.}
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------academic experience -----------------
\section{Academic Experience}
  \resumeSubHeadingListStart
    \resumeSubItem
      {Research Assistant, Integrative Biosensing Laboratory, U of Cincinnati}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Jan 2016 - Feb 2018}\\
      \vspace{10pt}
      {\textbf {\textit{Design and optimization of a Nanopore-based biosensor for sequence-specific nucleic acid detection.}}}{}
      \begin{itemize}[leftmargin=*]
      \vspace{-5pt}
      \setlength\itemsep{-0.1em}
        \item Developed a 97\%  efficient binary biosensor for quantitative estimation of the impact of electro-osmotic force.
         \item Impact of buffer concentration, field strength \& surface charges on the electrokinetics was studied with FEA.
         \item Successfully detected microRNA (miR-204 AND miR-210) related to clear cell renal cell carcinoma.
        \end{itemize}
       {\textbf{\textit {A Dielectrophoresis based Microfluidic device for Exosome isolation.}}}{}
        \begin{itemize}[leftmargin=*]
        \vspace{-5pt}
      \setlength\itemsep{-0.1em}
        \item Fabricated a particle isolator device in PDMS with a borosilicate pore as the collection zone using soft-lithography.
         \item Size selective trapping of exosomes from a matrix was demonstrated.
        \end{itemize}
        {\textbf {\textit{Microfabrication and characterization of a Piezo-resistive Pressure Sensor (MEMS).}}}{}
        \begin{itemize}[leftmargin=*]
        \vspace{-5pt}
      \setlength\itemsep{-0.1em}
        \item Microfabricated a pressure sensor prototype based on Wheatstone bridge arrangement on a 6” Silicon-wafer using photolithography and wet-etching techniques.
         \item Efficiency, hysteresis analysis, and linearity of the device were studied.
        \end{itemize}
    \resumeSubHeadingListEnd
    
    \resumeSubHeadingListStart
    \resumeSubItem
      {Teaching Assistant, Electrical Engg. \& Computer Science, U of Cincinnati}
      {~~~~~~~~~~~~~~~~~~~~~~~~~~Aug 2016 - May 2017}
      \vspace{5pt}
      \begin{itemize}[leftmargin=*]
      \vspace{-5pt}
      \setlength\itemsep{-0.1em}
        \item Designed and taught the class, ‘Biomicrofluidic Systems (laboratory) - EECE6078C’ encompassing COMSOL Multiphysics based FEA analysis and clean-room fabrication of active and passive microfluidic devices.
         \item Assisted students with review sessions in the class, ‘Biomedical Microsystems - EECE6007’, graded assignments.
        \end{itemize}
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Recent Publications \& Presentations}
\resumeSubHeadingListStart
\publication{Liu, X., Zimny, P., Zhang, Y., Rana, A., Nagel, R., Reisner, W., \& Dunbar, W. B. (2019). \textit{\textbf{Flossing DNA in a Dual Nanopore Device.}} Small, 1905379.}
\vspace{-5pt}
\publication{Rana, A., Zhang, Y. and Esfandiari, L., 2018. \textit{\textbf{Advancements in microfluidic technologies for isolation and early detection of circulating cancer-related biomarkers}}, Analyst.}
\vspace{-5pt}

\publication{Shi, L., Rana, A. and Esfandiari, L., 2018. \textit{\textbf{A low voltage nanopipette dielectrophoretic device for rapid entrapment of nanoparticles and exosomes extracted from plasma of healthy donors}}, Scientific reports (Nature).}
\vspace{-5pt}
\publication{Zhang, Y., Rana, A., Stratton, Y., Czyzyk-Krzeska, M.F. and Esfandiari, L., 2017.\textit{\textbf{ Sequence-Specific Detection of MicroRNAs Related to Clear Cell Renal Cell Carcinoma at fM Concentration by an Electroosmotically Driven Nanopore-Based Device}}, Analytical chemistry, 89(17), pp.9201-9208.}
\vspace{-5pt}
\publication{Poster: \textit{\textbf{A dielectrophoretic nanopore device with spatiotemporal resolution for microvesicles entrapment and quantification near living cells}}, The International Society for Extracellular Vesicles conf., May 2017, Toronto, ON.}
\vspace{-5pt}
\publication{Poster: \textit{\textbf{Impact of Electro-osmotic force in governing the motion of a charged species in a microfluidics based nanopore sensor}}, presented at Center for Advanced Design and Manufacturing of Integrated Microfluidics (CADMIM) – Industrial Advisory Board meeting, September 7, 2016, University of Cincinnati, OH.}
\vspace{-5pt}
\publication{Ghobadi, M., Zhang, Y., Rana, A., Esfahani, E.T. and Esfandiari, L., 2016, August. \textit{\textbf{Quantitative estimation of electro-osmosis force on charged particles inside a borosilicate resistive-pulse sensor}}, Engineering in Medicine and Biology Society (EMBC), 2016 IEEE 38th Annual International Conference of the (pp. 4228-4231). IEEE.}
\vspace{-5pt}
\resumeSubHeadingListEnd
\vspace{5pt}
%-----------LEADERSHIP ROLES, COMMUNITY ACTIVITIES AND AWARDS-----------------
\section{Leadership Roles, Community Activities \& Awards}
  \resumeSubHeadingListStart

\resumeSubheading
    {Save Our Shores - Beach Cleanup Drives}{Santa Cruz, CA}
    {Supporting the foundations of a thriving Monterey Bay: clean shores \& healthy habitats.}{Summer and Fall 2019}
\resumeSubheading
    {Clean Up Cincy}{Cincinnati, OH}
    {Cincinnati's largest student-led clean up program.}{Spring and Fall 2016}
    
	\resumeSubheading
    {University Graduate Scholarship (UGS) recipient}{Cincinnati, OH}
    {Partial tuition waiver awarded based on academic performance.}{Aug 2015 – Feb 2018}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {VP (Communications), The Techno-mentorship Establishment at UC}{Cincinnati, OH}
    {A platform to help students accomplish their entrepreneurial goals.}{May 2016 - May 2017}
\resumeSubHeadingListEnd
\end{document}
